---
title: "Introduction to TestTrek: Statistical Test Recommendations"
author: "Giovanni Briganti"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to TestTrek}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

## Introduction

`TestTrek` is a comprehensive R package designed to simplify the process of selecting the most appropriate statistical tests. Whether dealing with independent or dependent samples, `TestTrek` offers recommendations on statistical tests, effect sizes, and even post-hoc tests when necessary. 

## Installation

You can install `TestTrek` from your local setup (as it's not on CRAN yet):

```{r eval=FALSE}
# Install devtools if not already installed
# install.packages("devtools")

# Install TestTrek
devtools::install_local("/path_to_your_package/TestTrek")
```

Replace `/path_to_your_package/` with the actual path to your `TestTrek` package.

## Using TestTrek

### Recommending Tests for Independent Samples

To get recommendations for independent samples, simply provide your dataset and the two variables of interest:

```{r eval=FALSE}
library(TestTrek)

# Example usage with fictional data
# data <- read.csv("your_dataset.csv")
# recommend_test_independent(data, "variable1", "variable2")
```

### Recommending Tests for Dependent Samples

For dependent samples, the process is equally straightforward:

```{r eval=FALSE}
# Example usage with fictional data
# recommend_test_dependent(data, "variable1", "variable2")
```

## Conclusion

Selecting the right statistical test can often be a daunting task, especially for those not deeply versed in statistics. `TestTrek` aims to bridge this gap, providing clear recommendations and easing the analysis process. We hope you find `TestTrek` beneficial for your statistical adventures!
